%! Author = layne
%! Date = 4/12/26

% Preamble
%  preamble
\documentclass[14pt]{article}

% dependencies
\usepackage[margin=0.6in]{geometry}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{amsmath,amssymb}
\usepackage{tabularx}

% definitions
\definecolor{sky}{HTML}{EAF3FB}
\definecolor{navy}{HTML}{1F3A5F}
\definecolor{redbox}{HTML}{FCECEC}
\definecolor{greenbox}{HTML}{EDF8F0}
\definecolor{goldbox}{HTML}{FFF7E6}
\newtcolorbox{skillbox}[2][]{
    colback=#2,
    colframe=navy,
    boxrule=0.8pt,
    arc=2mm,
    left=2mm,right=2mm,top=1.5mm,bottom=1.5mm,
    fonttitle=\bfseries,
    title=#1,
}

\setlist[itemize]{leftmargin=1.2em,itemsep=0.35em,topsep=0.35em}
\setlist[enumerate]{leftmargin=1.4em,itemsep=0.35em,topsep=0.35em}


\begin{document}
    \begin{center}
    {\Large\bfseries Algebra 1 SOL: Desmos Reference Sheet} \\
    {\small \bfseries Three high-impact Desmos moves to help you ace your Algebra 1 SOL}
    \end{center}
    
    \vspace{0.5em}
    \begin{tcolorbox}[colback=sky,colframe=navy,boxrule=0.9pt,arc=2mm,left=2mm,right=2mm,top=1.5mm,bottom=1.5mm]
        \textbf{Core idea:} When you get stuck, \textbf{graph it, split it, or test values}.
        Desmos is strongest when you turn algebra into something visual or checkable.
    \end{tcolorbox}

    \vspace{0.5em}

    \begin{skillbox}[1. Simplify \& Evaluate Expressions]{greenbox}
        \textbf{If there is one variable:}
        \begin{itemize}
            \item Use \textbf{$x$}.
            \item Type the expression as a function: $f(x)= [expression]$.
            \item If a value is given, evaluate it with $f(value)$.
            \item If no value is given, graph the expression and compare it to the answer choices.
        \end{itemize}
        \textbf{If there is more than one variable:}
        \begin{itemize}
            \item Use variables such as \textbf{$a$, $b$, $c$}.
            \item Assign values like \textbf{$a=2$, $b=3$, $c=4$},
                    but do \textbf{not} use $-1$, $0$, or $1$.
            \item Evaluate the original expression and then test answer choices until one matches.
        \end{itemize}

        \textbf{Useful inputs:}
        \begin{itemize}
            \item \textbf{$ f(x)=3x^2-2x+5 $}
            \item \textbf{$ f(2) $}
            \item $a=2$ \hspace{1em} $b=3$
        \end{itemize}

        \textbf{Why avoid $-1$, $0$, $1$?} Those values can make different expressions look the same by accident.
    \end{skillbox}

    \begin{skillbox}[2. Equations \& Inequalities]{redbox}
        \textbf{If there is one variable:}
        \begin{itemize}
            \item Use \textbf{$x$}.
            \item Graph both sides as separate equations: $y=[left side]$ and $y=[right side]$.
            \item The \textbf{intersection} is the solution.
        \end{itemize}

        \textbf{If there are variables on both sides:}
        \begin{itemize}
            \item Split the equation into two lines.
            \item Check what the graphs do:
            \begin{itemize}
                \item intersect once $\rightarrow$ one solution
                \item parallel $\rightarrow$ no solution
                \item same line $\rightarrow$ infinite solutions
            \end{itemize}
        \end{itemize}

        \textbf{If an equation is set equal to 0:}
        \begin{itemize}
            \item Graph only the expression: $y=[expression]$.
            \item Look for \textbf{x-intercepts}.
            \item No x-intercept means \textbf{no real solution}.
        \end{itemize}

        \textbf{Inequalities:}
        \begin{itemize}
            \item Graph the inequality directly and use the shaded region.
        \end{itemize}
    \end{skillbox}

    \begin{skillbox}[3. Regressions for Linear Functions]{sky}
        \textbf{Use regression when you need the slope or equation of a line.}
        \begin{itemize}
            \item Enter two points in a table.
            \item Run linear regression using the regression utility
            \item Desmos will give you \textbf{$m$} and \textbf{$b$}.
        \end{itemize}

        \textbf{This is useful when:}
        \begin{itemize}
            \item you are given two points
            \item you can read two points from a graph
            \item the line is written in point-slope or standard form and you want slope-intercept form
        \end{itemize}

        \textbf{Strategy:}
        \begin{enumerate}
            \item Graph the line if needed.
            \item Pick two clear points on the line.
            \item Put them in a table.
            \item Use regression to get the equation.
        \end{enumerate}

        \textbf{Useful input:} $ y1~mx1+b $
    \end{skillbox}

        \begin{skillbox}[Quick Decision Guide]{goldbox}
            \begin{tabularx}{\linewidth}{>{\bfseries}p{0.28\linewidth}X}
            What am I trying to do? & Best Desmos move \\
            \hline
            \vspace{0.5em}

            Evaluate an expression & \vspace{0.5em} One variable? Make a function and plug in a value.  \\
            & Two or more variables?  Use a, b, c \\
            \hline
            \vspace{0.5em}

            Simplify or compare expressions & \vspace{0.5em} One variable? Graph and look for equivalence\\
            & Two variables? Use a, b, c and compare expression values\\
            \hline
            \vspace{0.5em}

            Factor a quadratic & \vspace{0.5em}use x and graph the quadratic then look for the zeros \\
            \hline
            \vspace{0.5em}

            Solve an equation & \vspace{0.5em} Graph both sides and find the intersection \\
            \hline
            \vspace{0.5em}

            Solve an equation set to 0 & \vspace{0.5em} Graph the expression and check x-intercepts \\
            \hline
            \vspace{0.5em}

            Find slope or line equation & \vspace{0.5em} Use two points and linear regression \\
            \end{tabularx}
        \end{skillbox}

    \begin{multicols}{2}
        \begin{skillbox}[High-Impact Reminders]{goldbox}
            \begin{itemize}
                \item Use \textbf{$x$} for single-variable work.
                \item Split equations into two sides when Desmos does not show the answer clearly.
                \item If you cannot see a solution, zoom out or check x-intercepts.
                \item Pick easy-to-read points when using regression.
                \item When in doubt: \textbf{graph it, split it, or test values}.
            \end{itemize}
        \end{skillbox}
\columnbreak
    \begin{skillbox}[Desmos Keyboard Shortcuts]{greenbox}
        \begin{itemize}
            \item sqrt = $\sqrt{}$
            \item cbrt = $\sqrt[3]{}$
            \item \^ = exponent
            \item $f(x) = x^2 \{x \ge 0\}$ domain restriction
            \item pi = $\pi$
            \item gcf(num1, num2, num3, \ldots) = greatest common factor
            \item lcm(num1, num2, num3, \ldots) = lowest common multiple
            \item round(num1, \# places) = round number to \# places
        \end{itemize}
    \end{skillbox}
    \end{multicols}

    \end{document}